---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
date: "October 17, 2014"
author: "Sam Dundon and Thierry Racaud"
output: html_document
bibliography:
  - Main.bib
---
* * * 
```{r echo=FALSE,cache=TRUE}
# Install necessary packages
library(maps)
library(mapdata)
```

*Introduction to Collaborative Social Science Data Analysis*

###Research Question  
Drawing a comparison between Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-focused, or focused on positive reinforcement - affect the rate of entrepreneurship in each country?

```{r echo=FALSE,cache=TRUE}
map('worldHires', 'sweden', col="gray90", fill=TRUE)

map('worldHires',
    c('UK', 'Ireland', 'Isle of Man','Isle of Wight','Wales:Anglesey'),
    xlim=c(-11,3), ylim=c(49,60.9),
    col="gray90", fill=TRUE)

map('worldHires','France', xlim=c(-8.2,8.5), ylim=c(42.2,51.1),
    col="gray90", fill=TRUE)

```

###Research Justification
Often, when it comes to public budgeting for education policies, the decision process does not appear to be rational. Very often, it does not seem to take into account the return on investment that should be expected in the long run. Perhaps this is because many policy makers have no inside knowledge of the field.  Thus, it may be that they do not have all of the neccesary tools or do not know how to assess the potential impact of their funding decisions, leading to the exclusion of this consideration from their decision-making process.


###Analytical Method
####Causal Chain

A higher degree of positive feedback and self-confidence reinforcement, either within organisations or directly between teachers and students is expected to positively impact both the  entrepreneurship rate and the rate of career-change within a given country.  

More group-oriented and team-building practices, either within organisations or as a staff strategy/policy towards students is expected to lead to more of the same supportive approach in a team member-manager context within a given country.  

If these assumptions are correct, the positive impact of these practices may increase productivity and country GDP. This project will identify variables that may be used to conduct this analysis and appropriate control variables to account for other business conditions and social conditions. The specific variables to trace this potential causal chain still need to be determined.


####Estimation Strategy  
The estimation strategy will consist of using cross-sectional data about Sweden, France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.

The dependent variable will be the rate of entrepreneurship with its related activities or attitudes as defined by the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org):

- Established Business Ownership Rate;   
- Entrepreneurial intention; and  
- Entrepreneurship as desirable career choice.  

The explanatory variables will be the sense of belonging to the group as defined by OECD [Program for International Student Assessment (PISA)](http://www.oecd.org/pisa/) (Data from 2012), the sense of individuality as an index constructed from [World Value Survey](http://www.worldvaluessurvey.org/wvs.jsp) items (Data from 2005 /2006), the degree of self confidence as an index again gathered from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).  

As mentioned above, we will need to control for the economic outlook at the time of data collection about entrepreneurship characteristics. We will also need to control for nine key entrepreneurship conditions as defined in the [National Experts Survey (NES)](http://www.gemiran.ir/sec/gem/?@=28) that may affect the rate of entrepreneurship. These nine conditions are the following:

1. Finance  
2. Government policies  
3. Government programmes  
4. Entrepreneurial Education and Training  
5. Research and Development Transfer (R & D)  
6. Commercial and professional infrastructure  
7. Internal Market openness  
8. Physical infrastructure and services  
9. Cultural and social norms  

The first step will be to see what the different behavioural and cultural patterns are in each country as observed among students. The differences observed may require some cultural explanations, including explanations regarding the type of welfare state in the given country.  

Then, should indeed different patterns be observed, we will need to proceed to an Ordinary Least Square (OLS) Regression in order to check to what extent these characteristics affect the rate of entrepreneurship in the country.  

Our main hypothesis would be that the more culturally group-oriented and the more self-confident a population is, the higher should entrepreneurship in that country be.  

Aside the sense of belonging as defined by OECD PISA study, here are some of the items from the World Value Survey 2005-2009 wave I could use to build the indexes about “sense of belonging to a group“, “sense of individuality” and “degree of self confidence”.  

###Concepts that I may need for my research

####Return on Investment
Self-confidence: It is difficult to obtain a credible measurement of self confidence, how should I measure this?  

Positive reinforcement is more easily defined but is also culture-dependent. Individual-focused systems vs group-oriented ones, how do you delimitate?  

Types of management

Return on Investment, how do you evaluate euros of tomorrow or value for money rate, perhaps using the social discount rate for some part, but also considering the potential GDP that could result from another education system management and culture vs what you would get carrying on like now.


```{r, echo=FALSE, include=FALSE, cache=TRUE}
# Install rempis from Christpher Gandrud's website
devtools::install_github('christophergandrud/repmis')
library(repmis)
# Load citation package
pkgs <- c('dplyr','ggplot2')
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

```

###Literature Review  

###References
