---
title: "The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis"
author: "Samuel Dundon and Thierry Racaud"
date: "November 14, 2014"
output: html_document
---

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

# Set working directory
setwd('~/Assign2Education/')

# Library Repmis, Tidy, Reshape2, and plyr packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)
library(WDI)
library(stargazer)
library(Zelig)

# Load citation package
pkgs <- c('repmis', 'tidyr', 'reshape2', 'plyr', 'WDI')
repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')

#### Import data from GEM Survey ####

# Import GEM fear of failure data
FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE) 

# Import GEM estblished entrepreneurship - current owner data
CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE) 

# Import GEM entrepreneurial intention data
EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE) 

# Import GEM nascent entrepreneur data
NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE) 

# Import GEM perceived capabilities data
PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE) 

# Import GEM perceived opportunities data as a proxy for potential control variables
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)

#### Clean data using tidy ####

### Clean FearFail ###
# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.

# Remove X's in FearFail year columns
names(FearFail) <- gsub("X", "", names(FearFail))


# Change years from columns to rows and create CFearFail
CFearFail <- melt(data = FearFail,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CFearFail <- plyr::rename(x = CFearFail, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentFear"))

### Clean CurrentOwner ###
# Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months

# Remove X's in CurrentOwner year columns
names(CurrentOwner) <- gsub("X", "", names(CurrentOwner))


# Change years from columns to rows and create CCurrentOwner
CCurrentOwner <- melt(data = CurrentOwner,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CCurrentOwner <- plyr::rename(x = CCurrentOwner, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentOwner"))

### Clean EntreIntention ###
# Percentage of 18-64 population (individuals involved in any stage of entrepenerurial activity excluded) who intend to start a business within three years.

# Remove X's in EntreIntention year columns
names(EntreIntention) <- gsub("X", "", names(EntreIntention))


# Change years from columns to rows and create CEntreIntention (No 2001 data available)
CEntreIntention <- melt(data = EntreIntention,
                  id.vars = c("Country"),
                  measure.vars = c("2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CEntreIntention <- plyr::rename(x = CEntreIntention, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentIntention"))

### Clean NascentEntre ###
# Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.

# Remove X's in NascentEntre year columns
names(NascentEntre) <- gsub("X", "", names(NascentEntre))


# Change years from columns to rows and create CNascentEntre
CNascentEntre <- melt(data = NascentEntre,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CNascentEntre <- plyr::rename(x = CNascentEntre, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentNascent"))

### Clean PerceivedCapabilities ###
# Percentage of 18-64 population who believe to have the required skills and knowledge to start a business

# Remove X's in PerceivedCapabilities year columns
names(PerceivedCapabilities) <- gsub("X", "", names(PerceivedCapabilities))

# Change years from columns to rows and create CPreceivedCapabilities
CPerceivedCapabilities<- melt(data = PerceivedCapabilities,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentPerceived"))

### Clean PerceivedOpportunities ###
# Percentage of 18-64 population who see good opportunities to start a firm in the area where they live

# Remove X's in PerceivedOpportunities year columns
names(PerceivedOpportunities) <- gsub("X", "", names(PerceivedOpportunities))

# Change years from columns to rows and create CPreceivedOpportunities
CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
                  id.vars = c("Country"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010", "2011", "2012",
                                   "2013"))

# Rename columns
CPerceivedOpportunities <- plyr::rename(x = CPerceivedOpportunities, 
                                      replace = c("variable" = "Year",
                                                  "value" = "PercentOpportunities"))

#### Merge the data ####
MergedGEM <- merge(CCurrentOwner, CEntreIntention,
                   union("Country", "Year"),
                   all = TRUE)

MergedGem2 <- merge(CFearFail, CNascentEntre,
                   union("Country", "Year"),
                   all = TRUE) 

MergedGem3 <- merge(CPerceivedCapabilities, MergedGEM,
                   union("Country", "Year"),
                   all = TRUE) 

MergedGem4 <- merge(MergedGem2, MergedGem3,
                   union("Country", "Year"),
                   all = TRUE) 

FinalGEM <- merge(MergedGem4, CPerceivedOpportunities,
                   union("Country", "Year"),
                   all = TRUE)

# Convert percent columns from character to numeric
FinalGEM[,"PercentPerceived"] <- as.numeric(FinalGEM[,"PercentPerceived"])
FinalGEM[,"PercentFear"] <- as.numeric(FinalGEM[,"PercentFear"])
FinalGEM[,"PercentNascent"] <- as.numeric(FinalGEM[,"PercentNascent"])
FinalGEM[,"PercentOwner"] <- as.numeric(FinalGEM[,"PercentOwner"])
FinalGEM[,"PercentIntention"] <- as.numeric(FinalGEM[,"PercentIntention"])
FinalGEM[,"PercentOpportunities"] <- as.numeric(FinalGEM[,"PercentOpportunities"])


#### Import WDI Annual GDP Growth Data ####
GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
                                                         'CL','CZ','DK','EE','FI','DE','HU', 
                                                         'IS','IE','IL','IT','JP','KR','LU',
                                                         'NL','NZ','NO','PL','PT','SK','SI',
                                                         'ES','SE','CH','TR','GB','US','GR'), 
                start=2001, end=2013)
# Rename columns
GDPGrowth <- plyr::rename(x = GDPGrowth, 
                                      replace = c("year" = "Year",
                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
                                                  "country" = "Country"))


# Recode country == "United States" to "United States of America" and Korea, Rep. to Korea (South)
GDPGrowth$Country[GDPGrowth$Country == "United States"] <- "United States of America"

# Recode country == "Korea, Rep."" to "Korea (South)"
GDPGrowth$Country[GDPGrowth$Country == "Korea, Rep."] <- "Korea (South)"

# Remove iso2c data to ease merge with FinalMerge data
GDPGrowth$iso2c <- NULL

# Merge GDPGrowth and FinalGEM
CompleteDataset <- merge(FinalGEM, GDPGrowth,
                   union("Country", "Year"),
                   all = TRUE) 

# Remove unncessary data from environment
remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)

# Check data to confirm change
summary(CompleteDataset)

# Run a linear regression
R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)

# Obtain summary statistics of R1
summary(R1)

# Calculate confidence intervals of R1
confint(R1)

# Run a linear regression of R2
R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)

# Obtain summary statistics of R2
summary(R2)

# Calculate confidence intervals of R2
confint(R2)

# Run a linear regression of R3
R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
 
# Obtain summary statistics of R3
summary(R3)

# Calculate confidence intervals of R3
confint(R3)

# Plot graph
car::scatterplotMatrix(CompleteDataset)
```                           

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'} 
# Create regression output table
labels <- c('Percent Perceived', 'Percent Fear',
            'Annual GDP Growth', 'Percent Opportunities', 'Percent Fear x Percent Opportunities','(Intercept)')

stargazer::stargazer(R1, R2, R3, covariate.labels = labels, 
                     title = 'Linear Regression Estimates', digits = 2, type = 'html')

```

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'}
library(Zelig)


Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, cite = FALSE,
            data = CompleteDataset, model = 'ls', param = function(z.out))

z5 <- zls$new()

summary(Z1)

Z1$sim()

sim(setz1)

```

*Introduction to Collaborative Social Science Data Analysis*

### Research Question

To what extent do the behavioural characteristics of education systems - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?

  
  
### Estimation Strategy

#### Causal Chain  

Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.

#### Data Collection

To find out, we need to gather quantitative data about entrepreneurship on the one hand, and some measures of these behavioural characteristics on the other hand.

##### The rate of entrepreneurship at country-level is the variable we intend to explain  


We intend to look into three dimensions of entrepreneurship. We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention. We will study them successively as we may well observe different effects.  

To measure these three dimensions of entrepreneurship, we will use three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:

- Established Business Ownership Rate (Percentage) 
- Nascent Entrepreneurship Rate (Percentage)
- Entrepreneurial intention Rate (Percentage)

We chose the GEM measure of entrepreneurship, as it is often referred to, especially in OECD studies.



##### Degree of Self-esteem reinforcement within the education system will be our key explanatory variable  


Inglehart showed how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) does shape the individual, especially in terms of self-esteem. Of course, is is not easy to quantify how supportive of students' self-esteem a given education system can be and we are still looking for the most adequate measure.  


The closest data we found so far is one of the six items / questions that GEM uses to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative".


For now, we use two GEM indicators that relate to self-esteem and confidence.

We look at the average "perceived capabilities" of an individual (18-64) of a given country to start a business. The data consists of average percentage at country-level.

We also take into account how the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur. The data consists of average percentage at country-level.  



##### We will include measures to check how individualistic and group-oriented a given education system is

Literature generally admits that self-confidence partly depends on the integration in social networks. Therefore, as we try to determine how supportive of students' self-esteem a given education system, we will look at how individualistic or group-oriented it is. To quantify such a behavioural feature is not easy, which is why we will have to rely on another measure: how individualistic or group-oriented an average student is by the end of compulsory education. Since OECD PISA collects data about students at the end of compulsory education, we will rely on "the sense of belonging" it defines.  



##### We will control for classic determinants of entrepreneurship  


We will intend to control for the classic determinants of entrepreneurship, that is for economic and structural determinants. More specifically, we will control for nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship. These nine conditions are the following:  

1. Finance  
2. Government policies  
3. Government programs  
4. Entrepreneurial Education and Training  
5. Research and Development Transfer (R & D)  
6. Commercial and professional infrastructure  
7. Internal Market openness  
8. Physical infrastructure and services  
9. Cultural and social norms

We are not yet fully sure on how best to control for all these variables, especially as GEM NES data does not seem to be available in dataset format as such. We may need to build up our own dataset, collecting data from the many national GEM NES reports. We will work on this in the coming weeks.  

As for now, as a substitute to all these conditions together, we use GEM indicator called "Perceived Opportunities". For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in. This is not equivalent to controlling for all the conditions above but it actually tells about all of them from the potential entrepreneur's point of view. Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the average 18-64-year-old individual of these countries.

Besides these nine conditions and the GEM "perceived opportunities" measure, we also intend to control for the economic outlook at the time of data collection which is why we chose to include GDP annual growth rate for each country from 2001 until 2013. This is our only data that does not originates from the GEM collection.  


#### Data Scraping and Cleaning  


In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:
GEM Established Entrepreneurship Rate
GEM Nascent Entrepreneurship Rate
GEM Entrepreneurial Intention
GEM Perceived Capabilities
GEM Fear of Failure
GEM Perceived Opportunities
GDP Annual Growth Rate

.




### Summary  


The impact of cultural factors in education on the rate of entrepreneurship in a given country is an important and under-researched topic that should be considered by policymakers constructing public education budgets. Through this project, we hope to encourage the consideration of these cultural factors by providing a qualitative and quantitative method for understanding the impact of these factors. Although several challenges remain to compiling the indexes discussed in this report, we are confident we can produce a helpful framework for examining and understanding these factors.


### References

>>>>>>> 648e7ea9f4a5614384d90351f0cd6454bd142647
